Robotic models of learning and development \\of speech and tool use.

### 2015-10-09 roadmap/doc.tex
experiments

		\begin{figure}[H]
			\centering
			\includegraphics[width=8cm]{./include/choice_test_choices.png}
			\includegraphics[width=8cm]{./include/choice_test_competences.png}
			%\includegraphics[width=8cm]{./include/choice_test_progresses.png}
			\caption{Progress on the 3 modules of a hierarchy with 2 choices of sub-modules for module 3. Left: Proportion of choices of module 3 (with a sliding window). Right: Competences (with a sliding window) babbled points of each modules.}
			\label{fchoices}
		\end{figure}

@@

@@

			\paragraph{}
			Different types of Top-Down Drive:
			\begin{itemize}
				\item Nothing,
				\item Exploration budget around goals asked by higher models,
				\item Balance self-computed interest with Top-Down interest (See Section \ref{tddkdtree}).
			\end{itemize}

			\paragraph{}
			Different types of Sensorimotor models:
			\begin{itemize}
				\item NN,
				\item LLWR,
				\item NSLWLR to handle non stationary forward models (See Section \ref{NSLWLR}).
			\end{itemize}

			\paragraph{}
			Different module implementations (implemented):
			\begin{itemize}
				\item Motor Babbling,
				\item SAGG-Random,
				\item SAGG-RIAC.
			\end{itemize}

@@

			\paragraph{}
			Different variables to test:
			\begin{itemize}
				\item Motor and Sensory dimensionalities,
				\item Type of functions: linear, cosine, geometric arm, non-continuous interaction with objects.
				\item Noise
			\end{itemize}

@@

				\paragraph{Experiment 1: Exploring in a structured hierarchy is more efficient than directly from $M$ to $S$.}
				\paragraph{}
				The idea is to compare our simplest algorithm (explore the module with higher progress) in a realistic setting (Hierarchy (a) of Fig. \ref{H}) to the control condition where a sensorimotor model is learned
				directly from the whole motor space $M$ to the whole sensori space $S$.

				\paragraph{Experiment 2: Which task should I explore now ?}
				\paragraph{}
				Here we compare the different possibilities to choose the module to explore in the hierarchy: maximizing the progress, maximizing with a bias towards lower-level modules, or use ZPDES,
				with the same hierarchy (a) of Fig. \ref{H}.

				\paragraph{Experiment 3: How to choose between different means to explore a given space ?}
				\paragraph{}
				Here we explain that we can choose between different means (e.g. different tools) using the one with the maximal competence.
				We can use the hierarchy (b) of Fig. \ref{H}.

				\paragraph{Experiment 4: How can high-level tasks guide the exploration of lower-level ones ?}
				\paragraph{}
				We compare different possibilities of Top-Down Guidance, 
				with hierarchy (c) of Fig. \ref{H}.

				\paragraph{Experiment 5: How can the system cope with perturbations on some of the forward models ?}
				\paragraph{}
				We apply perturbations to one of the possible forward models, either blocking, shifting or randomizing one dimension. 
				We can use the hierarchy (d) of Fig. \ref{H}.

		%
		\subsubsection{Measures}

			\begin{itemize}
				\item Exploration of each module,
				\item Exploration of top spaces,
				\item Competence of each sensorimotor model,
				\item Competence and Progress in each Interest Model,
				\item Developmental trajectories.
			\end{itemize}

>>>>

		\begin{figure}[H]
			\centering
			\includegraphics[width=8cm]{./include/choice_test_choices.png}
			\includegraphics[width=8cm]{./include/choice_test_competences.png}
			%\includegraphics[width=8cm]{./include/choice_test_progresses.png}
			\caption{Progress on the 3 modules of a hierarchy with 2 choices of sub-modules for module 3. Left: Proportion of choices of module 3 (with a sliding window). Right: Competences (with a sliding window) of babbled points of each modules.}
			\label{fchoices}
		\end{figure}

@@

			\paragraph{}
			Different module implementations (implemented):
			\begin{itemize}
				\item Motor Babbling,
				\item SAGG-Random.
			\end{itemize}

			\paragraph{}
			Different types of Sensorimotor models (implemented):
			\begin{itemize}
				\item NN or LWLR,
				\item NSLWLR to handle non stationary forward models (See Section \ref{NSLWLR}), or NSNN as NN plus a weighting by time.
			\end{itemize}

@@

			\paragraph{}
			Different types of Top-Down Drive:
			\begin{itemize}
				\item Just add noise to motor command of each module (pb: interferes with competence and progress estimation)  (implemented),
				\item Exploration budget around goals asked by higher models (explonential in $levels^{n+1}$ so even $n=1$ is not feasible in general but maybe in practice)  (implemented),
				\item Exploration budget only for the modules one layer below the babbling module (not implemented).
				\item Balance self-computed interest with Top-Down interest (See Section \ref{tddkdtree}, not implemented).
			\end{itemize}

@@

			\paragraph{}
			Different variables to test: motor and sensory dimensionalities, type of functions (linear, cosine, geometric arm, non-continuous interaction with objects), noise.

			\paragraph{Possible arm models:}
			\begin{itemize}
				\item $n$ DOFs 2D geometric arm
			\end{itemize}

			\paragraph{Possible tool models:}
			\begin{itemize}
				\item static piano
				\item stick 
			\end{itemize}

			\paragraph{Possible object models:}
			\begin{itemize}
				\item static object with features depending on the piano
				\item dynamic object
			\end{itemize}

@@

				% Experiment 1
				\paragraph{Experiment 1: Exploring in a structured hierarchy is more efficient than directly from $M$ to $S$.}				
				\begin{itemize}
					\item Idea: to compare our simplest algorithm (explore the module with higher progress) in a realistic setting (Hierarchy (a) of Fig. \ref{H}) to the control condition where a sensorimotor model is learned
							directly from the whole motor space $M$ to the whole sensori space $S$.

					\item Conditions: Hierarchy (a) vs $M \rightarrow S$, Motor Babbling vs SAGG-Random

					\item Features: MAB on all modules, NN, No TDD.

					\item Measures: exploration of intermediate spaces (hands, tools), exploration of top spaces (objects). Competence to reach random goals in reachable parts of intermediate and top spaces. 
							Statistics on multiple runs to see regularity/diversity in developmental trajectories.
				\end{itemize}

				% Experiment 2
				\paragraph{Experiment 2: Which task should I explore now ?}
				\begin{itemize}
					\item Idea: to compare the different possibilities to choose the module to explore in the hierarchy: maximizing the progress, maximizing with a bias towards lower-level modules, or use ZPDES,
							with the same hierarchy (a) of Fig. \ref{H}.

					\item Conditions: Random module, MAB on all modules, MAB with bias, ZPDES.

					\item Features: Hierarchy (a), SAGG-Random, NN, No TDD.

					\item Measures: exploration of intermediate spaces (hands, tools), exploration of top spaces (objects). Competence to reach random goals in reachable parts of intermediate and top spaces. 
							Statistics on multiple runs to see regularity/diversity in developmental trajectories.
				\end{itemize}

				% Experiment 3
				\paragraph{Experiment 3: How to choose between different means to explore a given space ?}
				\begin{itemize}
					\item Idea: to explain how we can choose between different means (e.g. different tools) using the one with the maximal competence, or maximal progress.
							We can use the hierarchy (b) of Fig. \ref{H}, in order to have 2 different tools to move the object.

					\item Conditions: maximize competence vs progress, noise on each tool, reachability (e.g. size) of each tool.

					\item Features: Hierarchy (b), MAB on all modules, SAGG-Random, NN, No TDD.

					\item Measures: exploration of intermediate spaces (hand, tools), exploration of top spaces (object). Competence to reach random goals in reachable parts of intermediate and top spaces. 
							Statistics on multiple runs to see regularity/diversity in developmental trajectories.
				\end{itemize}

				% Experiment 4
				\paragraph{Experiment 4: How can high-level tasks guide the exploration of lower-level ones ?}
				\begin{itemize}
					\item Idea: tocompare different possibilities of Top-Down Guidance, with hierarchy (c) of Fig. \ref{H} in order to have TD guidance at different levels: 
							arm with one higher model, hand with 2 higher models, tool1 with one higher model, or tool2 with 2 higher models.

					\item Conditions: No TDD, Just add noise to motor command of each module (pb: interferes with competence estimation) 
							vs explore $n$ points and returns the best (warning: exponential)
							vs only one layer below the babbling module explores $n$ points.

					\item Features: Hierarchy (c), MAB on all modules with bias (or no bias?), SAGG-Random, NN.

					\item Measures: exploration of intermediate spaces (hands, tools), exploration of top spaces (objects). Competence to reach random goals in reachable parts of intermediate and top spaces. 
							Statistics on multiple runs to see regularity/diversity in developmental trajectories.
				\end{itemize}

				% Experiment 5
				\paragraph{Experiment 5: How can the system cope with perturbations on some of the forward models ?}
				\begin{itemize}
					\item Idea: to apply perturbations to one of the possible forward models, either blocking, shifting or randomizing one dimension. 
							We can use the hierarchy (d) of Fig. \ref{H} in order to see an adaptation at 2 levels: the use of one hand to use one tool, the use of both tools to move the object even if only one is perturbated.

					\item Conditions: No perturbations, which model is perturbated (arm, tool), type of perturbation (blocking, shifting, random).

					\item Features: Hierarchy (d), MAB on all modules, SAGG-Random, NN, best TDD.

					\item Measures: exploration of intermediate spaces (hands, tools) and top spaces (objects) before and after perturbations. 
							Competence to reach random goals in reachable parts of intermediate and top spaces before and after perturbations. 
							Statistics on multiple runs to see regularity/diversity in developmental trajectories.
				\end{itemize}
